### 2016-07-18 P4-Explore-and-Summarize-Data/submission.Rmd
Update submission.Rmd

```{r }
quality_plot <- function(x, y, ylab) {
  return (ggplot(data = rw, aes(x, y)) +
           geom_boxplot(fill = 'green') +
            xlab('quality') +
            ylab(ylab) + 
            facet_wrap(~quality))
}

grid.arrange(quality_plot(rw$quality, rw$fixed.acidity, 'fixed.acidity (g / dm^3)'),
             quality_plot(rw$quality, rw$volatile.acidity, 
                          'volatile.acidity (g / dm^3)'),
             quality_plot(rw$quality, rw$citric.acid, 'citric.acid (g / dm^3)'),
             quality_plot(rw$quality, rw$residual.sugar, 'residual.sugar (g / dm^3)'),
             quality_plot(rw$quality, rw$chlorides, 'chlorides (g / dm^3)'),
             quality_plot(rw$quality, rw$free.sulfur.dioxide, 
                          'free.sulfur.dioxide (mg / dm^3)'),
             quality_plot(rw$quality, rw$total.sulfur.dioxide, 
                          'total.sulfur.dioxide (mg / dm^3)'),
             quality_plot(rw$quality, rw$density, 
                          'density (g / cm^3)'),
             quality_plot(rw$quality, rw$pH, 'pH'),
             quality_plot(rw$quality, rw$sulphates, 'sulphates (g / dm^3)'),
             quality_plot(rw$quality, rw$alcohol, 'alcohol (% volume)'),
             ncol = 4)
```

@@

grid.arrange(rating_plot(rw$rating, rw$fixed.acidity, 'fixed.acidity (g / dm^3)'),
             rating_plot(rw$rating, rw$volatile.acidity, 
                         'volatile.acidity (g / dm^3)'),
             rating_plot(rw$rating, rw$citric.acid, 'citric.acid (g / dm^3)'),
             rating_plot(rw$rating, rw$residual.sugar, 'residual.sugar (g / dm^3)'),
             rating_plot(rw$rating, rw$chlorides, 'chlorides (g / dm^3)'),
             rating_plot(rw$rating, rw$free.sulfur.dioxide, 
                         'free.sulfur.dioxide (mg / dm^3)'),
             rating_plot(rw$rating, rw$total.sulfur.dioxide, 
                         'total.sulfur.dioxide (mg / dm^3)'),
             rating_plot(rw$rating, rw$density, 'density (g / cm^3)'),
             rating_plot(rw$rating, rw$pH, 'pH'),
             rating_plot(rw$rating, rw$sulphates, 'sulphates (g / dm^3)'),
             rating_plot(rw$rating, rw$alcohol, 'alcohol (% volume)'),
             ncol = 4)
```

@@

# Reflection
After this EDA, I can conclude that the major factors for better wine quality is alcohol, acidity and sulphates. These features must be in required content otherwise negative impact will effect the wine quality. Also, we can't be totally sure about quality index also it has been taken some experts. We've also concluded that there is linear relationship between pH and quality with negative slope.

>>>>

```{r }
quality_plot <- function(x, y, ylab) {
  return (ggplot(data = rw, aes(as.factor(x), y)) +
           geom_boxplot(fill = 'green') +
            xlab('quality') +
            ylab(ylab))
}

grid.arrange(quality_plot(rw$quality, rw$fixed.acidity, 'fixed.acidity (g / dm^3)'),
             quality_plot(rw$quality, rw$volatile.acidity, 
                          'volatile.acidity (g / dm^3)'),
             quality_plot(rw$quality, rw$citric.acid, 'citric.acid (g / dm^3)'),
             quality_plot(rw$quality, rw$residual.sugar, 'residual.sugar (g / dm^3)'),
             quality_plot(rw$quality, rw$chlorides, 'chlorides (g / dm^3)'),
             quality_plot(rw$quality, rw$free.sulfur.dioxide, 
                          'free.sulfur.dioxide (mg / dm^3)'),
             quality_plot(rw$quality, rw$total.sulfur.dioxide, 
                          'total.sulfur.dioxide (mg / dm^3)'),
             quality_plot(rw$quality, rw$density, 
                          'density (g / cm^3)'),
             quality_plot(rw$quality, rw$pH, 'pH'),
             quality_plot(rw$quality, rw$sulphates, 'sulphates (g / dm^3)'),
             quality_plot(rw$quality, rw$alcohol, 'alcohol (% volume)'),
             quality_plot(rw$quality, rw$total.acidity, 'alcohol (% volume)'),
             ncol = 4)
```

@@

grid.arrange(rating_plot(rw$rating, rw$fixed.acidity, 'fixed.acidity (g / dm^3)'),
             rating_plot(rw$rating, rw$volatile.acidity, 
                         'volatile.acidity (g / dm^3)'),
             rating_plot(rw$rating, rw$citric.acid, 'citric.acid (g / dm^3)'),
             rating_plot(rw$rating, rw$residual.sugar, 'residual.sugar (g / dm^3)'),
             rating_plot(rw$rating, rw$chlorides, 'chlorides (g / dm^3)'),
             rating_plot(rw$rating, rw$free.sulfur.dioxide, 
                         'free.sulfur.dioxide (mg / dm^3)'),
             rating_plot(rw$rating, rw$total.sulfur.dioxide, 
                         'total.sulfur.dioxide (mg / dm^3)'),
             rating_plot(rw$rating, rw$density, 'density (g / cm^3)'),
             rating_plot(rw$rating, rw$pH, 'pH'),
             rating_plot(rw$rating, rw$sulphates, 'sulphates (g / dm^3)'),
             rating_plot(rw$rating, rw$alcohol, 'alcohol (% volume)'),
             rating_plot(rw$rating, rw$total.acidity, 'alcohol (% volume)'),
             ncol = 4)
```

### Mean of variables for *ideal* rating

```{r}
mean <- c(mean(subset(rw, rating == 'ideal')$fixed.acidity),
          mean(subset(rw, rating == 'ideal')$volatile.acidity),
          mean(subset(rw, rating == 'ideal')$citric.acid),
          mean(subset(rw, rating == 'ideal')$residual.sugar),
          mean(subset(rw, rating == 'ideal')$chlorides),
          mean(subset(rw, rating == 'ideal')$free.sulfur.dioxide),
          mean(subset(rw, rating == 'ideal')$total.sulfur.dioxide),
          mean(subset(rw, rating == 'ideal')$density),
          mean(subset(rw, rating == 'ideal')$pH),
          mean(subset(rw, rating == 'ideal')$sulphates),
          mean(subset(rw, rating == 'ideal')$alcohol),
          mean(subset(rw, rating == 'ideal')$total.acidity))

names(mean) <- c('fixed.acidity', 'volatile.acidity', 'citric.acid',
                         'residual.sugar', 'chlorides', 'free.sulfur.dioxide',
                         'total.sulfur.dioxide', 'density', 'pH',
                         'sulphates', 'alcohol', 'total.acidity')

mean
```

### Median of variables for *ideal* rating

```{r}
median <- c(median(subset(rw, rating == 'ideal')$fixed.acidity),
          median(subset(rw, rating == 'ideal')$volatile.acidity),
          median(subset(rw, rating == 'ideal')$citric.acid),
          median(subset(rw, rating == 'ideal')$residual.sugar),
          median(subset(rw, rating == 'ideal')$chlorides),
          median(subset(rw, rating == 'ideal')$free.sulfur.dioxide),
          median(subset(rw, rating == 'ideal')$total.sulfur.dioxide),
          median(subset(rw, rating == 'ideal')$density),
          median(subset(rw, rating == 'ideal')$pH),
          median(subset(rw, rating == 'ideal')$sulphates),
          median(subset(rw, rating == 'ideal')$alcohol),
          median(subset(rw, rating == 'ideal')$total.acidity))

names(median) <- c('fixed.acidity', 'volatile.acidity', 'citric.acid',
                         'residual.sugar', 'chlorides', 'free.sulfur.dioxide',
                         'total.sulfur.dioxide', 'density', 'pH',
                         'sulphates', 'alcohol', 'total.acidity')

median
```

@@

# Reflection
So, there are lots of features on which the wine quality is depend. We do a lot to find the relationship between every variables in the dataset, try to get some linear relation using geom_smooth().  
And, after this EDA, I can conclude that the major factors for better wine quality is alcohol, acidity and sulphates. These features must also be in required content otherwise negative impact will effect the wine quality. Also, we can't be totally sure about quality index also it has been taken by some experts. We've also concluded that there is linear relationship between pH and quality with negative slope.
